Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-11-08 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Fix footnote about omitted Axiom 2 in proof of lemma 1 and write about the need for Axioms 2 and 3 in the proof of Anderson’s lemma 1.

Because of Anderson's emendations to Axiom 1 and Definition 1, the proof of Lemma 1 has to be modified as well.
The proof shown below has been modified as little as possible. Interestingly, in order to eliminate 
the extra box modality in Anderson's emended Definition D\ref{A:D1}, the modified proof below uses the modal axiom T.

@@

%implication for equivalence in essence: 
%\begin{small}
\begin{prooftree}
\AXC{Axiom \ref{A:A3}} \dashedLine
\UIC{$P(G)$}
\AXC{$ $} \RightLabel{5}
\UIC{$\nec  \forall y. (G(y)\imp \varphi(y))$}\RightLabel{$\wedge_I$}
\BIC{$P(G)\wedge \nec  \forall y. (G(y)\imp \varphi(y))$}\RightLabel{$\imp_E$}
\AXC{Axiom \ref{A:A2}} \dashedLine
\UIC{\ldots\footnote{The formulas are ommitted here due to lack of space.}} \doubleLine \RightLabel{$\all_E$ x 2}
\UIC{\ldots}
\BIC{$P(\varphi)$}
\AXC{$\subproof_{11}$} \dashedLine 
\UIC{$  G(\gamma)$} \dottedLine \RightLabel{D\ref{A:D1}}
\UIC{$ \all \varphi. (P(\varphi)\biimp \nec \varphi(\gamma))$}  \RightLabel{$\all_E$}
\UIC{$ P(\varphi)\biimp \nec \varphi(\gamma)$}  \RightLabel{$\biimp_E$}
\BIC{$ \nec \varphi(\gamma)$} \RightLabel{$\imp_I^5$}
\UIC{$[\subproof_{14}] \quad \nec  \forall y. (G(y)\imp \varphi(y))\imp \nec \varphi(\gamma)$}
\end{prooftree}
%\end{small}

>>>>

Because of Anderson's emendations to Axiom 1 and Definitions 1 and 2, the proof of Lemma 1 has to be modified\footnote{Due to lack of space, the instantiation of Axiom \ref{A:A2} are ommitted in the emended proof of Lemma \ref{A:L1}.} as well.
The proof shown below has been modified as little as possible. Interestingly, in order to eliminate 
the extra box modality in Anderson's emended Definition \ref{A:D1}, the modified proof below uses the modal axiom T. 
Likewise, to obtain the extra box in the emended Definition \ref{A:D2}, Axioms 2 and 3 were used.

@@

%implication for equivalence in essence: 
%\begin{small}
\begin{prooftree}
\AXC{Axiom \ref{A:A3}} \dashedLine
\UIC{$P(G)$}
\AXC{$ $} \RightLabel{5}
\UIC{$\nec  \forall y. (G(y)\imp \varphi(y))$}\RightLabel{$\wedge_I$}
\BIC{$P(G)\wedge \nec  \forall y. (G(y)\imp \varphi(y))$}\RightLabel{$\imp_E$}
\AXC{Axiom \ref{A:A2}} \dashedLine
\UIC{.} \doubleLine \RightLabel{$\all_E$ x 2}
\UIC{.}
\BIC{$P(\varphi)$}
\AXC{$\subproof_{11}$} \dashedLine 
\UIC{$  G(\gamma)$} \dottedLine \RightLabel{D\ref{A:D1}}
\UIC{$ \all \varphi. (P(\varphi)\biimp \nec \varphi(\gamma))$}  \RightLabel{$\all_E$}
\UIC{$ P(\varphi)\biimp \nec \varphi(\gamma)$}  \RightLabel{$\biimp_E$}
\BIC{$ \nec \varphi(\gamma)$} \RightLabel{$\imp_I^5$}
\UIC{$[\subproof_{14}] \quad \nec  \forall y. (G(y)\imp \varphi(y))\imp \nec \varphi(\gamma)$}
\end{prooftree}
%\end{small}
